Exploring Local Explanations of Non-linear Models Using Animated Linear Projections

### 2022-01-16 _paper.rmd
SHAP wordsmithing and plot size.

```{r shapdistrbd, echo=F, fig.align='center', out.width="60%", fig.cap = "Illustration of the use of SHAP values for a random forest model for salaries of FIFA 2020 players based on nine predictors corresponding to different skills. A star offensive and defensive player are compared, L. Messi and V. van Dijk, respectively. Panel (a) shows breakdown plot of three seqences of the features, order and magnitude change. Panel (b) shows the distribution of attribution for each feature across 25 seqences of predictors, with the mean displayed as a dot, for each players. Offense and movement are important for Messi but not van Dijk, and conversely, defense and power are important for van Dijk but not Messi."}
knitr::include_graphics("./figures/shap_distr_bd.png")
```

>>>>

```{r shapdistrbd, echo=F, fig.align='center', out.width="100%", fig.cap = "Illustration of the use of SHAP values for a random forest model for salaries of FIFA 2020 players based on nine predictors corresponding to different skills. A star offensive and defensive player are compared, L. Messi and V. van Dijk, respectively. Panel (a) shows breakdown plot of three seqences of the features, order and magnitude change. Panel (b) shows the distribution of attribution for each feature across 25 seqences of predictors, with the mean displayed as a dot, for each players. Offense and movement are important for Messi but not van Dijk, and conversely, defense and power are important for van Dijk but not Messi."}
knitr::include_graphics("./figures/shap_distr_bd.png")
```
